\renewcommand{\bibname}{References}
\begin{thebibliography}{Abc 99}

\bibitem[App 10]{iphoneimagesource} {\sl Apple IPhone Gallery}, Available at:\\
http://www.apple.com/iphone/gallery/, 7 may 2010.

\bibitem[Cau 92]{Cau92} Caudell, T.P. and Mizell, D.W: {\sl Augmented reality: an application of heads-up display technology to manual manufacturing processes}, Res. \& Technol., Boeing Comput. Services, Seattle, January 1992.

\bibitem[Erl 10]{Erl10} {\sl Erlang Reference Manual}, Available at:\\
http://www.erlang.org/doc/, 7 may 2010.

\bibitem[Fle 09]{Fle09}Fleckenstein, S. and Preston-Werner, T.: {\sl Erlectricity}, Available at:\\
http://github.com/mojombo/erlectricity/, 7 may 2010.

\bibitem[Hay 09]{Hay09} Hayes, G.: {\sl 16 top Augmented Reality business models}, Available at:\\
http://www.personalizemedia.com/16-top-augmented-reality-business-models/, 7 may 2010.

\bibitem[Mil 94]{Mil94} Milgram, P., H. Takemura, et al.: {\sl Augmented Reality: A Class of Displays on the Reality-Virtuality Continuum.} SPIE Proceedings: Telemanipulator and Telepresence Technologies . H. Das, SPIE. 2351 : 282-292, 1994.

\bibitem[Mne 10]{Mne10}{\sl Mnesia Reference Manual}, Available at:\\
http://www.erlang.org/doc/apps/mnesia/, 7 may 2010.

\bibitem[Nok 10]{Nok10}{\sl Nokogiri}, Available at:\\
http://nokogiri.org/, 7 may 2010.

\bibitem[Sut 68]{Sut68} Sutherland, I. E.: {\sl A head-mounted three dimensional display}, Proceedings of the December 9-11, 1968, fall joint computer conference, part I, San Francisco, California,  December 1968.

\bibitem[Tel 05]{headupsource}Telstar Logistics:  {\sl C-130J: Co-pilot's head-up display panel}, Available at:\\
http://www.flickr.com/photos/telstar/4136242/, 7 may 2010.

\end{thebibliography}
